---
title: "NBAmodel"
author: "Moisey Aalaev"
date: "5/14/2021"
output: pdf_document
---

NOTE:
THIS RMD CONTAINS THREE DIFFERENT RMD FILES THAT WERE COPY AND PASTED INTO THIS ONE BECAUSE ONLY ONE
FILE SUBMISSION WAS ALLOWED ON CCLE.

```{r}
train <- read.csv("NBATrain.csv")
test <- read.csv("NBATestNoY.csv")
#attach(train)
dim(test)
names(train)
head(train)
```


=========================================================== CREATING NEW VARIABLES =====================================================
Country
```{r}
train$NBA_Country <- ifelse(train$NBA_Country == "USA", "Native", "Foreign")
#test1$NBA_Country <- ifelse(test1$NBA_Country == "USA", "Native", "Foreign")
table(train1$NBA_Country)

summary(lm(train$Salary ~ train$NBA_Country, data=train))
```

MarketTeams
```{r}
bigMarketTM <- c("CLE", "POR", "LAC", "SAS", "MEM", "TOR", "DET", "ORL", "WAS", "CHA")
medMarketTM <- c("NYK", "DAL", "NOP", "GSW", "MIA", "ATL", "MIL", "SAC", "LAL", "BOS")

train$MarketVal1 <- ifelse(train$TM %in% bigMarketTM, "BigMarket", ifelse(train$TM %in% medMarketTM, "medMarket", "smallMarket"))
#train$MarketVal1 <- ifelse(train$TM %in% bigMarketTM, "BigMarket",  "smallMarket")

```

Status
```{r}
summary(train$Salary)

train$Status <- ifelse(train$PTS >= 24 , "All-star", ifelse(train$PTS >= 19, "Good", "Bad"))
table(train$Status)

test$Status <- ifelse(test$PTS >= 24, "All-star", ifelse(test$PTS >= 19, "Good", "Bad"))
table(test$Status)
```

AGE
```{r}
train$Age <- ifelse((train$Age >= 24 & train$Age <= 28), "Prime", ifelse(train$Age > 28 , "Old", "Young"))
table(train$Age)

test$Age <- ifelse((test$Age >= 24 & test$Age <= 28), "Prime", ifelse(test$Age > 28 , "Old", "Young"))

table(test1$Age)
```

BPM
```{r}
summary(train$BPM)
train$BPM <- ifelse(train$BPM >= 2, "GOAT",ifelse(train$BPM >= 0, "Good", "Meh"))


test$BPM <- ifelse(test$BPM >= 2, "GOAT",ifelse(test$BPM >= 0, "Good", "Meh"))

summary(lm(Salary~train$BPM, data=train))
table(train$BPM)
```

```{r}
summary(train$MP)
dummy <- ifelse(train$MP >= 1783.0, "Lots",ifelse(train$MP >= 1089.5, "Average", "Low"))
# 
# 
# test$BPM <- ifelse(test$BPM >= 2, "GOAT",ifelse(test$BPM >= 0, "Good", "Meh"))

summary(lm(Salary~dummy, data=train))
# table(train$MP)
```

```{r}
train$dummy <- ifelse(train$TM == "DAL", "DAL",ifelse(train$TM == "LAC", "LAC", "other"))
summary(lm(Salary~dummy, data=train))
```

```{r}
summary(lm(Salary~Status, data=train))
```

=================================================== INITAL STEP FUNCTION MODEL =================================================

```{r}
m00 <- lm(Salary~1,data=train)
mfull <- lm(Salary~.+TopBracket, data=train)

forwardAIC <- step(m00, scope=list(lower=~1,upper=mfull),
                    direction="forward", data=train)
backAIC <- step(mfull, direction="backward", data=train)

forwardBIC <- step(mBest2, scope=list(lower=~1,upper=mfull),
                   direction="forward", data=train, k = log(length(train[,1])))

backBIC <- step(mfull, direction="backward", data=train, k=log(length(train[,1])))
```

```{r}
summary(backAIC)
summary(forwardAIC)
summary(backBIC)
summary(forwardBIC)
```
    
```{r}
#TopBracket<- c(TopBracket, TRUE)
TopBracket <-c()
TopBracket <- ifelse(train$Salary >= 9532681, TRUE,  FALSE)

logReg <- glm(formula = TopBracket ~ FT + GS + VORP + USG. + FG + G + Age + MP + T.Div + Pos+BPM,
    family = binomial, data=train)


# test$TopBracket <- ifelse(predict(logReg, data=test) >= 0, TRUE, FALSE)

#Y.hat <- predict(mBest, data=train, newdata = test)

probs <- predict(logReg, train, type="response")

pred <- rep("No",dim(train)[1])
pred[probs>.5] <- "Yes"
train$TopBracket <- pred
probs <- predict(logReg, test, type="response")

pred <- rep("No",dim(test)[1])
pred[probs>.5] <- "Yes"
test$TopBracket <- pred
summary(lm(Salary ~train$TopBracket, data=train))
```
    
```{r}
mBest <- forwardAIC
mBest<-update(mBest, ~.-NBA_Country)
mBest<-update(mBest, ~.-TM)
mBest<-update(mBest, ~.+MarketVal)
summary(mBest)
vif(mBest)
```
.6142, 0.6271 0.6215 
```{r}
summary(backAIC)
summary(forwardAIC)
summary(lm(train$Salary ~ Status, data=train))
```

```{r}
backAIC <- step(mBest, direction="backward", data=train) #FT + G + Age + MP + BPM + TopBracket
summary(backAIC)
mBest2 <- backAIC

backBIC <- step(mBest, direction="backward", data=train, k=log(length(train[,1]))) #FT + VORP + G + Age + MP + TopBracket
summary(backBIC)
```


```{r}
mBest<-update(mBest, ~.-NBA_Country)
mBest <- update(mBest, ~.-Ob)
mBest <- update(mBest, ~.G)
mBest <- update(mBest, ~.-BLK)
mBest <- update(mBest, ~.+Pos)
mBest <- update(mBest, ~.+BPM)
mBest <- update(mBest, ~.-DBPM)
mBest <- update(mBest2, ~+T.Div)
# -G, Blk, blk.,stl., ob, ws
summary(mBest2)
```
OG-----0.6409,	Adjusted R-squared:  0.6142, 390 DF
no Ob--0.6406,	Adjusted R-squared:  0.6149
no G-- 0.6079,	Adjusted R-squared:  0.5809
no blk--0.6073,	Adjusted R-squared:  0.5814
no blk.--- 0.6005,	Adjusted R-squared:  0.5752

no WS ---0.5994,	Adjusted R-squared:  0.5751
with G -- 0.634,	Adjusted R-squared:  0.6108 
noFG--0.6328,	Adjusted R-squared:  0.6105
no X2P.--0.6311,	Adjusted R-squared:  0.6097
no DBPM --0.6255,	Adjusted R-squared:  0.6048
no Ortg -- 0.6252,	Adjusted R-squared:  0.6054
yes DBPM,ODPM----0.6348,	Adjusted R-squared:  0.6126
no DBPM --- 0.6332,	Adjusted R-squared:  0.611
no ODPM--- 0.6334,	Adjusted R-squared:  0.6121
no stl. --0.6161,	Adjusted R-squared:  0.5999
T.div --0.6324,	Adjusted R-squared:  0.612

TRIMMING DOWN USING CORR
```{r}
corr <- cor(cbind(train$Salary, train$FT, train$GS, train$G, train$MP, train$VORP, train$Ortg, train$USG., train$FG, 
                    train$BPM, train$DBPM, train$ODPM))
corrplot.mixed(corr, lower="number", upper="pie")
cor(train$Salary, train$AGE, use = "complete.obs")


```

================================================================== SUBMISSION ===========================================================

```{r}
Y.hat <- predict(mBest2, data=train, newdata = test)
Y.hat <- abs(Y.hat)
sub <- data.frame(1:180, Y.hat)
sub
colnames(sub)[1] <- "Ob"
colnames(sub)[2] <- "Salary"
 

write.csv(sub, file="sub8.csv")

#rebounds, fouls, and assists 
```

Sub4 : 
Multiple R-squared:  0.6977,	Adjusted R-squared:  0.653, 365 DF
Multiple R-squared:  0.6309,	Adjusted R-squared:  0.6104 397 DF


mBest: Salary ~ FT + GS + Pos + VORP + T.Div + USG. + FG + 
    STL. + G + Age + MP + BPM

============================================================= OG MODELS ============================================================

```{r}
#WS + FT + GS + G + TM + MP + Pos + AST + VORP
m0 <- lm(Salary~ TM + AST + FG + Pos + MP + Rk+ G + GS + Ortg + WS + VORP + FT*PTS, data=train)
summary(m0) 
vif(m0)
```

```{r}
par(mfrow=c(2,2))
plot(m0)
```

```{r}
pairs(Salary~ AST + FG + MP + Rk+ G + GS + Ortg + WS + VORP + FT*PTS)

corr <- cor(cbind(Salary, AST, FG, MP, Rk, G, GS,  Ortg, WS, VORP, FT*PTS))
corr
corrplot.mixed(corr, lower="number", upper="pie")
head()
```


```{r}
m00 <- lm(Salary~1,data=train)

forwardAIC <- step(m00, scope=list(lower=~1,
upper=~ TM + AST + FG + Pos + MP + Rk+ G + GS + Ortg + WS + VORP + FT*PTS),
direction="forward", data=train)
```

```{r}


 if(min(FG) <= 0)
   FG = FG+10^-6

 min(FG)

summary(powerTransform(cbind(FG)~1))


#TM + AST + FG + Pos + MP + Rk + G + GS + VORP + FT + PTS + FT*PTS

# Salary=1.3, AST=.42, FG=.7, MP=.5, G=1, GS=.14, FT=.42, VORP=-.5,
# FT=.42, PTS=.68, FT*PTS=.28

summary(mBest)

mTrans <- lm(Salary ~ TM + sqrt(AST) + FG + Pos + sqrt(MP) + G + log(GS) + FT + VORP + FT + sqrt(PTS))
summary(mTrans)

mBest <- mTrans
```
#if we do log of y , we do inverse of log (exp) on the predicted y that we submit!


```{r}
par(mfrow=c(2,2))
plot(mBest)
```




============================================================================= SECOND .RMD FILE BELOW ===============================================================
---
title: "splitNBAdata "
author: "Moisey Alaev"
output: pdf_document
---

NOTE:
CONTAINS CODE FOR WORKING WITH SPLIT TRAINING DATA INTO NEW LOCAL
TRAINING SET AND TESTING SET

========================================================= DATA SET UP ===========================================================
```{r}
train <- read.csv("NBATrain.csv")
test <- read.csv("NBATestNoY.csv")
dim(train)
#detach(train)
dim(test)
names(train)
head(train)
```

SPLIT DATA INTO TRAINING AND TEST
```{r}
set.seed(12345)
smp_size <- floor(0.70 * nrow(train))
smp_size

train_ind <- sample(seq_len(nrow(train)), size = smp_size)
train1 <- train[train_ind, ]
test1 <- train[-train_ind, ]
```

```{r}
c <- ggplot(data=train1, aes(Salary))
c + geom_histogram() + ggtitle("Distribution of Salary") + theme(plot.title = element_text(hjust = 0.5))
# dim(train)
# dim(train1)
# dim(test1)

d <- ggplot(data=test1, aes(Salary))
d + geom_histogram() + ggtitle("Distribution of Salary") + theme(plot.title = element_text(hjust = 0.5))

```
=================================================== CREATING NEW VARIABLES =====================================================
COUNTRY
```{r}
train1$NBA_Country <- ifelse(train1$NBA_Country == "USA", "Native", "Foreign")
test1$NBA_Country <- ifelse(test1$NBA_Country == "USA", "Native", "Foreign")
table(train1$NBA_Country)
```

ALLSTAR
```{r}
# train1$Status <- ifelse(train1$Salary >= 10077571, "All-star", ifelse(train1$Salary >= 4017759 , "Starter", "Bench"))
# table(train1$Status)
# test1$Status <- ifelse(test1$Salary >= 8557872, "All-star", ifelse(test1$Salary >= 3253242, "Starter", "Bench"))

train1$Status <- ifelse(train1$PTS >= 24 , "All-star", ifelse(train1$PTS >= 19, "Good", "Bad"))
table(train1$Status)

test1$Status <- ifelse(test1$PTS >= 24, "All-star", ifelse(test1$PTS >= 19, "Good", "Bad"))
table(test1$Status)

```

AGE
```{r}
# max(train1$Age)
# min(train1$Age)
#train1$Age
train1$Age <- ifelse((train1$Age >= 24 & train1$Age <= 28), "Prime", ifelse(train1$Age > 28 , "Old", "Young"))
table(train1$Age)

test1$Age <- ifelse((test1$Age >= 24 & test1$Age <= 28), "Prime", ifelse(test1$Age > 28 , "Old", "Young"))
table(test1$Age)
summary(lm(Salary~Age, data=train))
```

TM CONVERSION
```{r}
# bigMarketTM <- c("CLE", "POR", "LAC", "SAS", "MEM", "TOR", "DET", "ORL", "WAS", "CHA")
# medMarketTM <- c("NYK", "DAL", "NOP", "GSW", "MIA", "ATL", "MIL", "SAC", "LAL", "BOS")
# smallMarketTM <- c("CHI","OKC",  "HOU", "IND", "PHX", "PHI", "DEN", "MIN", "BKN",  "UTA")
# train1$TM <- ifelse(is.element(train1$TM, bigMarketTM), "BigMarket", ifelse(train1$TM %in% medMarketTM, "medMarket", "smallMarket"))

# 
# bigMarketTM <- c("CLE", "POR", "LAC", "SAS", "MEM", "TOR", "DET", "ORL", "WAS", "CHA", "NYK", "DAL", "NOP", "GSW", "MIA")
# smallMarketTM <- c("CHI","OKC",  "HOU", "IND", "PHX", "PHI", "DEN", "MIN", "BKN",  "UTA", "ATL", "MIL", "SAC", "LAL", "BOS")

train1$TM <- ifelse(train1$TM %in% bigMarketTM, "BigMarket", "smallMarket")


# dummy <- ifelse(train1$TM %in% bigMarketTM, "yo", ifelse(train1$TM %in% medMarketTM, "medMarket", "smallMarket"))
# 
# table(as.factor(dummy))
# 
# class(train1$TM)
table(train1$TM)
summary(lm(Salary~TM, train1))
```

ROLES <- GAMES STARTED 
```{r}
summary(train$GS)
# GS 
train1$Role <- ifelse(train1$GS >= 48 , "Starter", ifelse(train$GS > 8 , "SecondUp", "Bench"))
table(train1$Role)

test1$Role <- ifelse(test1$GS >= 41 , "Starter", "Bench") #ifelse(train$GS > 10 , "SecondUp"
table(test1$Role)
```

BPM
```{r}
# BPM made into catagories
train1$BPM <- ifelse(train1$BPM >= 2, "GOAT",ifelse(train1$BPM >= 0, "Good", "Meh"))
test1$BPM <- ifelse(test1$BPM >= 2, "GOAT",ifelse(test1$BPM >= 0, "Good", "Meh"))
table(train1$BPM)
```

TopBracket
```{r}
# logestic regression to predict if player in top 25 percent
TopBracket <-c()
TopBracket <- ifelse(train1$Salary >= 9532681, TRUE,  FALSE)

logReg <- glm(formula = TopBracket ~ FT + GS + VORP + USG. + FG + G + Age + MP + T.Div + Pos + BPM,
    family = binomial, data=train1)

probs <- predict(logReg, train1, type="response")

pred <- rep("No",dim(train1)[1])
pred[probs>.5] <- "Yes"
train1$TopBracket <- pred

preds <- rep("No",126)
preds[probs[1:126]>.5] <- "Yes"
test1$TopBracket <- preds
```

====================================================== TESTING NEW VARIABLES =====================================================

```{r}
#summary(lm(Salary ~ train1$PTS, data=train1))
#summary(lm(Salary ~ Age, data=train1))
summary(lm(Salary ~ train1$Role, data=train1))
summary(lm(Salary ~ train1$GS, data=train1))
```

=================================================== INITAL STEP FUNCTION MODEL =================================================

AIC
```{r}
# inital model and full model
mfull <- lm(Salary~., data=train1)
m0 <- lm(Salary~1, data=train1)

#Inital model using foward and backward step
forwardAIC <- step(m0, scope=list(lower=~1, upper=mfull), direction="forward", data=train1)
backAIC <- step(mfull, direction="backward", data=train1)

forwardBIC <- step(m0, scope=list(lower=~1,upper=mfull),direction="forward", data=train, k = log(length(train1[,1])))
backBIC <- step(mfull, direction="backward", data=train, k=log(length(train1[,1])))
```

```{r}
summary(backAIC)
summary(forwardAIC)
summary(backBIC)
summary(forwardBIC)
#mBest <- forwardAIC
vif(backAIC)
vif(forwardAIC)
vif(backBIC)
vif(forwardBIC)
#anova(forwardAIC, backAIC)
mBest <- lm(Salary ~ FT + G + Age + MP + BPM + TopBracket, data=train1)
summary(mBest)
length(mBest$coefficients)
```
============================================================== Testing Vars ====================================================

```{r}
#summary(lm(Salary ~ train1$GS, data=train1))
summary(train$GS)
```


```{r}
forwardAIC <- update(forwardAIC, ~.-NBA_Country)
```

```{r}
length(mBest$coefficients)
```


========================================================== Transformations ===================================================

```{r}

```


================================================ COMPARE PREDICTED Y TO TEST DATA =============================================
forwardAIC= 0.4827242, 0.540341
backAIC = 0.5180431, 0.5327286
backBIC = 0.4741212, 0.4551961
forwardBIC = 0.4682725, 0.4700264
```{r}
Yhat <- predict(forwardAIC, data=train1, newdata = test1)
cor(test1$Salary, abs(Yhat), use = "complete.obs")^2
```
```{r}
Predicted.Salary <- abs(predict(mBest, data=train1, newdata = test1))
cor(test1$Salary, Y.hat, use = "complete.obs")^2
ggplot(aes(y=Predicted.Salary, x=Salary), data=test1) + geom_point() + geom_smooth(method = "lm") +
  ggtitle("Relationship between Actual Salary and Predicted Salary") + theme(plot.title = element_text(hjust = 0.5)) +
  annotate("text", x = (1.8*10^7), y=(2.2*10^7), label = "Correlation Coefficent: 0.527402")
```




============================================================================ THIRD .RMD FILE BELOW ==================================================================
---
title: "VisualsforReport"
author: "Moisey Alaev"
date: "6/14/2021"
---

NOTE;
CONTAINS CODE USED FOR VISUALS FOR THE FINAL REPORT

```{r}
train <- read.csv("NBATrain.csv")
test <- read.csv("NBATestNoY.csv")
attach(train)
dim(train)
```

```{r}

# Age made into catagories
train$Age <- ifelse((Age >= 24 & Age <= 28), "Prime", ifelse(Age > 28 , "Old", "Young"))
table(Age)

# BPM made into catagories
train$BPM <- ifelse(BPM >= 2, "GOAT",ifelse(BPM >= 0, "Good", "Meh"))
table(BPM)

# logestic regression to predict if player in top 25 percent
TopBracket <-c()
TopBracket <- ifelse(train$Salary >= 9532681, TRUE,  FALSE)

logReg <- glm(formula = TopBracket ~ FT + GS + VORP + USG. + FG + G + Age + MP + T.Div + Pos+BPM,
    family = binomial, data=train)

probs <- predict(logReg, train, type="response")

pred <- rep("No",dim(train)[1])
pred[probs>.5] <- "Yes"
train$TopBracket <- pred
```


```{r}
mBest <- lm(formula = Salary ~ FT + G + Age + MP + BPM + TopBracket, data = train)
```


```{r}
a <- ggplot(data=train, aes(Salary))
a + geom_histogram() + ggtitle("Distribution of Salary") + theme(plot.title = element_text(hjust = 0.5))

b <- ggplot(data=train, aes(log(Salary)))
b + geom_histogram() + ggtitle("Distribution of log(Salary)") + theme(plot.title = element_text(hjust = 0.5))
```

```{r}
num_pred <- cbind()
num_pred <- unlist(lapply(train, is.character)) #ifelse(unlist(lapply(train, is.numeric)), num_predictors <- cbind(num_pred, ))
numerical.vars <- train[ , num_pred]
numerical.vars
#adply(cor(Salary, numerical.vars, use = "complete.obs"), 2)
levels(as.factor(T.Div))

```

```{r}
corrs <- cor(cbind(PTS,Salary, MP, OWS, DWS, WS, VORP, GS, FT))
corrplot.mixed(corrs, upper="number", lower="pie")
```

```{r}
g <- ggplot(data=train,aes(y=Salary, x=T.Conf))
g + geom_boxplot() + ggtitle("Conference vs Salary") + theme(plot.title = element_text(hjust = 0.5))
```
```{r}
table(as.factor(NBA_Country))
```

```{r}
train$NBA_Country_temp <- ifelse(train$NBA_Country == "USA", "Native", "Foreign")
#test1$NBA_Country <- ifelse(test1$NBA_Country == "USA", "American", "Foreign")

summary(lm(Salary ~ NBA_Country, data=train))
summary(lm(Salary ~ NBA_Country_temp, data=train))
```

```{r}
bigMarketTM <- c("CLE", "POR", "LAC", "SAS", "MEM", "TOR", "DET", "ORL", "WAS", "CHA", "NYK", "DAL", "NOP", "GSW", "MIA")
medMarketTM <- c("NYK", "DAL", "NOP", "GSW", "MIA", "ATL", "MIL", "SAC", "LAL", "BOS")

#MarketVal1 <- ifelse(train$TM %in% bigMarketTM, "BigMarket", ifelse(train$TM %in% medMarketTM, "medMarket", "smallMarket"))
MarketVal1 <- ifelse(train$TM %in% bigMarketTM, "BigMarket",  "smallMarket")
summary(lm(Salary ~ MarketVal1))
```
```{r}
Role <- ifelse(train$GS >= 49 , "Starter", ifelse(train$GS > 11 , "SecondUp", "Bench"))
summary(lm(train$Salary~Role, data=train))
```

```{r}
corr <- cor(cbind(FT, Salary, WS, Age, USG., GS, G, FTA, DBPM, BLK., X2P, STL., DRB, Ortg, DRB, Rk, OWS))
# corr <- cor(cbind(train$Salary, train$FT, train$GS, train$G, train$MP, train$VORP, train$Ortg, train$USG., train$FG, 
#                     train$BPM, train$DBPM, train$ODPM))
corrplot.mixed(corr, upper="number", lower="pie")
```
```{r}
summary(lm(Salary ~ FT + G + Age + MP + BPM + TopBracket, data=train))
```

```{r}
library(gridExtra)

diagPlot<-function(model) {
  p1<-ggplot(model, aes(model$fitted, model$residuals),label=rownames(bonds))+geom_point()
  p1<-p1+stat_smooth(method="loess")+geom_hline(yintercept=0, col="red", linetype="dashed")
  p1<-p1+xlab("Fitted values")+ylab("Residuals")
  p1<-p1+ggtitle("Residual vs Fitted Plot")+theme_bw()
  p2<-ggplot(model,aes(sample=rstandard(model))) + stat_qq() + stat_qq_line()
  p2<-p2+xlab("Theoretical Quantiles")+ylab("Standardized Residuals")
  p2<-p2+ggtitle("Normal Q-Q")
  p3<-ggplot(model, aes(model$fitted, sqrt(abs(rstandard(model)))))+geom_point(na.rm=TRUE)
  p3<-p3+stat_smooth(method="loess", na.rm = TRUE)+xlab("Fitted Value")
  p3<-p3+ylab(expression(sqrt("|Standardized residuals|")))
  p3<-p3+ggtitle("Scale-Location")+theme_bw()+geom_hline(yintercept=sqrt(2),col="red", linetype="dashed")
  p4<-ggplot(model, aes(seq_along(cooks.distance(model)), cooks.distance(model)))+geom_bar(stat="identity", position="identity")
  p4<-p4+xlab("Obs. Number")+ylab("Cook's distance")
  p4<-p4+ggtitle("Cook's distance")+theme_bw()+geom_hline(yintercept=4/(length(model$residuals-2)), col="red", linetype="dashed")
  
  p5<-ggplot(model, aes(hatvalues(model), rstandard(model)))+geom_point(aes(size=cooks.distance(model)), na.rm=TRUE)
  p5<-p5+stat_smooth(method="loess", na.rm=TRUE)
  p5<-p5+xlab("Leverage")+ylab("Standardized Residuals")
  p5<-p5+ggtitle("Residual vs Leverage Plot")
  p5<-p5+scale_size_continuous("Cook's Distance", range=c(1,5))
  p5<-p5+theme_bw()+theme(legend.position="bottom")+geom_hline(yintercept=c(-2,2),col="red",linetype="dashed")+geom_vline(xintercept=4/(length(model$residuals)), col="blue", linetype="dashed")+ylim(-4,4)
  p6<-ggplot(model, aes(hatvalues(model), cooks.distance(model)))+geom_point(na.rm=TRUE)+stat_smooth(method="loess", na.rm=TRUE)
  p6<-p6+xlab("Leverage hii")+ylab("Cook's Distance")
  p6<-p6+ggtitle("Cook's dist vs Leverage")
  p6<-p6+geom_abline(slope=seq(0,3,0.5), color="gray", linetype="dashed")
  p6<-p6+theme_bw()
  return(grid.arrange(p1,p2,p3,p4,p5,p6,ncol=3))
}

```


```{r}
temp <- lm(Salary ~FT + G + Age + MP + BPM + TopBracket, data=train)
diagPlot(temp)
```

```{r}
inverseResponsePlot(mBest)
```
```{r}
ggplot(aes(y=Salary, x=1:420), data=train) + geom_point() +  geom_smooth(method='lm', formula=  Salary ~ FT + G + Age + MP + BPM + TopBracket)
plot(mBest)

```

```{r}
#mmps(mBest, vars=~MP)#c(FT, G, MP))
mmp(mBest,MP,xlab="MP", main= "      MMP of the Minutes Played")
mmp(mBest,MP,xlab="G", main= "      MMP of the Games Played")
mmp(mBest,MP,xlab="FT", main= "      MMP of the Free Throws")
```
```{r}
leveragePlots(mBest)
```

```{r}
n = 300
hvals <- hatvalues(mBest)
rstandard <- rstandard(mBest)
cutoff <- 2*(7/480)

#qplot(cleveland$patientnum, hvals) + geom_hline(yintercept = 4/n)
OUT <- ifelse(hvals >= cutoff, "yes", "no")
LEV <- ifelse(abs(rstandard) >= 2, "yes", "no")

table(LEV, OUT)


# Get leverage points and test them

which(hats > cutoff) 

# Get standardized residuals for testing leverage type

which(abs(rStand) > 2) # outliers


which((hats > cutoff) & (abs(rStand) > 2)) # bad leverages

which((rStand > cutoff) & (abs(rStand) < 2)) # good leverages
```

```{r}
anova(mBest)
```

