---
title: "splitNBAdata "
author: "Moisey Alaev"
output: pdf_document
---

========================================================= DATA SET UP ===========================================================
```{r}
train <- read.csv("NBATrain.csv")
test <- read.csv("NBATestNoY.csv")
dim(train)
#detach(train)
dim(test)
names(train)
head(train)
```

SPLIT DATA INTO TRAINING AND TEST
```{r}
set.seed(12345)
smp_size <- floor(0.70 * nrow(train))
smp_size

train_ind <- sample(seq_len(nrow(train)), size = smp_size)
train1 <- train[train_ind, ]
test1 <- train[-train_ind, ]
```

```{r}
c <- ggplot(data=train1, aes(Salary))
c + geom_histogram() + ggtitle("Distribution of Salary") + theme(plot.title = element_text(hjust = 0.5))
# dim(train)
# dim(train1)
# dim(test1)

d <- ggplot(data=test1, aes(Salary))
d + geom_histogram() + ggtitle("Distribution of Salary") + theme(plot.title = element_text(hjust = 0.5))

```
=================================================== CREATING NEW VARIABLES =====================================================
COUNTRY
```{r}
train1$NBA_Country <- ifelse(train1$NBA_Country == "USA", "Native", "Foreign")
test1$NBA_Country <- ifelse(test1$NBA_Country == "USA", "Native", "Foreign")
table(train1$NBA_Country)
```

ALLSTAR
```{r}
# train1$Status <- ifelse(train1$Salary >= 10077571, "All-star", ifelse(train1$Salary >= 4017759 , "Starter", "Bench"))
# table(train1$Status)
# test1$Status <- ifelse(test1$Salary >= 8557872, "All-star", ifelse(test1$Salary >= 3253242, "Starter", "Bench"))

train1$Status <- ifelse(train1$PTS >= 24 , "All-star", ifelse(train1$PTS >= 19, "Good", "Bad"))
table(train1$Status)

test1$Status <- ifelse(test1$PTS >= 24, "All-star", ifelse(test1$PTS >= 19, "Good", "Bad"))
table(test1$Status)

```

AGE
```{r}
# max(train1$Age)
# min(train1$Age)
#train1$Age
train1$Age <- ifelse((train1$Age >= 24 & train1$Age <= 28), "Prime", ifelse(train1$Age > 28 , "Old", "Young"))
table(train1$Age)

test1$Age <- ifelse((test1$Age >= 24 & test1$Age <= 28), "Prime", ifelse(test1$Age > 28 , "Old", "Young"))
table(test1$Age)
summary(lm(Salary~Age, data=train))
```

TM CONVERSION
```{r}
# bigMarketTM <- c("CLE", "POR", "LAC", "SAS", "MEM", "TOR", "DET", "ORL", "WAS", "CHA")
# medMarketTM <- c("NYK", "DAL", "NOP", "GSW", "MIA", "ATL", "MIL", "SAC", "LAL", "BOS")
# smallMarketTM <- c("CHI","OKC",  "HOU", "IND", "PHX", "PHI", "DEN", "MIN", "BKN",  "UTA")
# train1$TM <- ifelse(is.element(train1$TM, bigMarketTM), "BigMarket", ifelse(train1$TM %in% medMarketTM, "medMarket", "smallMarket"))

# 
# bigMarketTM <- c("CLE", "POR", "LAC", "SAS", "MEM", "TOR", "DET", "ORL", "WAS", "CHA", "NYK", "DAL", "NOP", "GSW", "MIA")
# smallMarketTM <- c("CHI","OKC",  "HOU", "IND", "PHX", "PHI", "DEN", "MIN", "BKN",  "UTA", "ATL", "MIL", "SAC", "LAL", "BOS")

train1$TM <- ifelse(train1$TM %in% bigMarketTM, "BigMarket", "smallMarket")


# dummy <- ifelse(train1$TM %in% bigMarketTM, "yo", ifelse(train1$TM %in% medMarketTM, "medMarket", "smallMarket"))
# 
# table(as.factor(dummy))
# 
# class(train1$TM)
table(train1$TM)
summary(lm(Salary~TM, train1))
```

ROLES <- GAMES STARTED 
```{r}
summary(train$GS)
# GS 
train1$Role <- ifelse(train1$GS >= 48 , "Starter", ifelse(train$GS > 8 , "SecondUp", "Bench"))
table(train1$Role)

test1$Role <- ifelse(test1$GS >= 41 , "Starter", "Bench") #ifelse(train$GS > 10 , "SecondUp"
table(test1$Role)
```

BPM
```{r}
# BPM made into catagories
train1$BPM <- ifelse(train1$BPM >= 2, "GOAT",ifelse(train1$BPM >= 0, "Good", "Meh"))
test1$BPM <- ifelse(test1$BPM >= 2, "GOAT",ifelse(test1$BPM >= 0, "Good", "Meh"))
table(train1$BPM)
```

TopBracket
```{r}
# logestic regression to predict if player in top 25 percent
TopBracket <-c()
TopBracket <- ifelse(train1$Salary >= 9532681, TRUE,  FALSE)

logReg <- glm(formula = TopBracket ~ FT + GS + VORP + USG. + FG + G + Age + MP + T.Div + Pos + BPM,
    family = binomial, data=train1)

probs <- predict(logReg, train1, type="response")

pred <- rep("No",dim(train1)[1])
pred[probs>.5] <- "Yes"
train1$TopBracket <- pred

preds <- rep("No",126)
preds[probs[1:126]>.5] <- "Yes"
test1$TopBracket <- preds
```

====================================================== TESTING NEW VARIABLES =====================================================

```{r}
#summary(lm(Salary ~ train1$PTS, data=train1))
#summary(lm(Salary ~ Age, data=train1))
summary(lm(Salary ~ train1$Role, data=train1))
summary(lm(Salary ~ train1$GS, data=train1))
```

=================================================== INITAL STEP FUNCTION MODEL =================================================

AIC
```{r}
# inital model and full model
mfull <- lm(Salary~., data=train1)
m0 <- lm(Salary~1, data=train1)

#Inital model using foward and backward step
forwardAIC <- step(m0, scope=list(lower=~1, upper=mfull), direction="forward", data=train1)
backAIC <- step(mfull, direction="backward", data=train1)

forwardBIC <- step(m0, scope=list(lower=~1,upper=mfull),direction="forward", data=train, k = log(length(train1[,1])))
backBIC <- step(mfull, direction="backward", data=train, k=log(length(train1[,1])))
```

```{r}
summary(backAIC)
summary(forwardAIC)
summary(backBIC)
summary(forwardBIC)
#mBest <- forwardAIC
vif(backAIC)
vif(forwardAIC)
vif(backBIC)
vif(forwardBIC)
#anova(forwardAIC, backAIC)
mBest <- lm(Salary ~ FT + G + Age + MP + BPM + TopBracket, data=train1)
summary(mBest)
length(mBest$coefficients)
```
============================================================== Testing Vars ====================================================

```{r}
#summary(lm(Salary ~ train1$GS, data=train1))
summary(train$GS)
```


```{r}
forwardAIC <- update(forwardAIC, ~.-NBA_Country)
```

```{r}
length(mBest$coefficients)
```


========================================================== Transformations ===================================================

```{r}

```


================================================ COMPARE PREDICTED Y TO TEST DATA =============================================
forwardAIC= 0.4827242, 0.540341
backAIC = 0.5180431, 0.5327286
backBIC = 0.4741212, 0.4551961
forwardBIC = 0.4682725, 0.4700264
```{r}
Yhat <- predict(forwardAIC, data=train1, newdata = test1)
cor(test1$Salary, abs(Yhat), use = "complete.obs")^2
```
```{r}
Predicted.Salary <- abs(predict(mBest, data=train1, newdata = test1))
cor(test1$Salary, Y.hat, use = "complete.obs")^2
ggplot(aes(y=Predicted.Salary, x=Salary), data=test1) + geom_point() + geom_smooth(method = "lm") +
  ggtitle("Relationship between Actual Salary and Predicted Salary") + theme(plot.title = element_text(hjust = 0.5)) +
  annotate("text", x = (1.8*10^7), y=(2.2*10^7), label = "Correlation Coefficent: 0.527402")
```

